Discrepancy, Coresets, and Sketches in Machine Learning

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
Adding weak coresets and doubling dimension
Added future work comment

The set $Q_\eps$ is an $\eps$-net for $\Q$. 
It is a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$. 
We note that the size $|Q_\eps|$ is often exponential in the problem parameters. 
Nevertheless, our dependence on the failure probability is \emph{doubly} logarithmic. 
This means the dependence on the problem parameters is still only polylogarithmic.
The above improves on the well-known merge-and-reduce tree construction by \cite{BENTLEY1980301}.
Moreover, it is quite likely that a uniform $\eps$-net for $\Q$ for the sake of minimization (ERM on the final sketch).
See literature on weak coresets and concentration results based on doubling dimensions for Lipchitz functions. \todo{add citation}

>>>>

The set $Q_\eps$ is an $\eps$-net for $\Q$. 
It is a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$. 
We note that the size $|Q_\eps|$ is often exponential in the problem parameters. 
Nevertheless, our dependence on the failure probability is \emph{doubly} logarithmic. 
This means the dependence on the problem parameters is still only polylogarithmic.
The above improves on the well-known merge-and-reduce tree construction by \cite{BENTLEY1980301}.
Moreover, it is likely that a uniform $\eps$-net for $\Q$ is not required for the sake of minimization (ERM on the final sketch).
See literature on weak coresets and (e.g. \cite{Feldman:2007:PKC:1247069.1247072}) concentration results based on doubling dimensions in classification/query space \cite{BSHOUTY2009323}. The refinement of the above results is left for future work.
